An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-27 4_method.tex
w_pref ==> w_*

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^\sim_v = 2 R(v) / w_\text{pref},
\label{eq:initialBeadCount}
\end{equation}
where $w_\text{pref}$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting polygon points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_\text{pref}^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_\text{pref}$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

\paragraph{Quantization}
We define a quantization operator $q$ to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
$q(d) = \left\lfloor d / w_\text{pref} + \nicefrac12 \right\rfloor$.
Alternative quantization schemes will be discussed in \cref{sec_generalization}.
By applying $q$ to the heights of central nodes we quantize the bead count:
$b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor$.
\iffalse
Along with this quantization, an amendment to the marking filtering is performed, in order to alleviate a problem that will be handled in \cref{section_beading_conflicts}.
Specifically, unmarked regions are marked as central if they lie between two nodes with the same integer bead count.
\fi
%We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
% From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
% If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

@@

A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
The transition is centered at the anchor, and its length is set to $t(n) = w_\text{pref}$.
We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes which are in between the two ends of the transition by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}).
%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
%compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the ST by adding support edges at the transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_{pref}$ for long stretches with ramps in between.

>>>>

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^\sim_v = 2 R(v) / w_*,
\label{eq:initialBeadCount}
\end{equation}
where $w_*$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting polygon points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_*^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_*$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.pdf}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

\paragraph{Quantization}
We define a quantization operator $q$ to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
$q(d) = \left\lfloor d / w_* + \nicefrac12 \right\rfloor$.
Alternative quantization schemes will be discussed in \cref{sec_generalization}.
By applying $q$ to the heights of central nodes we quantize the bead count:
$b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor$.
\iffalse
Along with this quantization, an amendment to the marking filtering is performed, in order to alleviate a problem that will be handled in \cref{section_beading_conflicts}.
Specifically, unmarked regions are marked as central if they lie between two nodes with the same integer bead count.
\fi
%We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
% From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
% If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

@@

A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
The transition is centered at the anchor, and its length is set to $t(n) = w_*$.
We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes which are in between the two ends of the transition by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}).
%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
%compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the ST by adding support edges at the transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_*$ for long stretches with ramps in between.

### 2019-08-27 5_generalization.tex
w_pref ==> w_*

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( q^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_\text{pref}$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
The toolpath locations $L$ ensure that beads are extruded from the center of where they end up, that the beads don't overlap and that the symmetry restrictions are met.

\paragraph{Uniform beading scheme}
We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
t(n) &= 0 \\
q(d) &=
\begin{cases}
1 & \text{ if } d < w_\text{pref} \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_\text{pref} & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_\text{pref} / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

\begin{align*}
t(n) &= \frac12 w_\text{pref} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
q(d) &= q^-(d) +
\begin{cases}
-1 & \text{ if } q^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  q^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{General distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w_\text{pref} + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.

\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
E(n,d) &= d - n w_\text{pref} \\
W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.

>>>>

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w_* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d_\text{max}^\text{unmarked} &= w_* \\ 
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_* \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( q^{-1}(n) / w_*  - n \right) \\
t(n) &= w_* \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
The toolpath locations $L$ ensure that beads are extruded from the center of where they end up, that the beads don't overlap and that the symmetry restrictions are met.

\paragraph{Uniform beading scheme}
We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
W(n,d)_i &= w_* \text{ for all } i 
%\\
%L(n,d)_i &= w_* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
t(n) &= 0 \\
q(d) &=
\begin{cases}
1 & \text{ if } d < w_* \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_* & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_* / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_*$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_*$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

\begin{align*}
t(n) &= \frac12 w_* \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
q(d) &= q^-(d) +
\begin{cases}
-1 & \text{ if } q^-(d) w_* - d > w_* - r_\text{max} \\
1  & \text{ if }  q^-(d) w_* - d < w_* - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_* &\text{ if } i = \frac12 (n-1) \\
w_* &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_* \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{General distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w_* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.

\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
E(n,d) &= d - n w_* \\
W(n,d)_i &= w_* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.

### 2019-08-27 6_validation.tex
w_pref ==> w_*

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

@@

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
We set the preferred width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

>>>>

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w_*] = \SI{0.4}{\milli\meter}$.

@@

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
We set the preferred width to $w_* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
